Nested Sampling with Multiple Objective Functions

### 2018-06-16 doc/ms.tex
Results figures for demo problem

>>>>

The algorithm was run for 1000 reps, to a `depth' of 500 nats,
with 100 particles and 1000 MCMC steps per NS iteration per rep.
Results are given in
Figures~\ref{fig:demo_logZ_H},~\ref{fig:demo_residuals},
and~\ref{fig:demo_N_eff}.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{figures/demo_logZ_H.pdf}
\caption{The partition function $\ln(Z)$ and information $H$ as a function
of the two temperatures, reconstructed using the algorithm. Compare with
Figure~\ref{fig:demo_truth}.
\label{fig:demo_logZ_H}}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{figures/demo_residuals.pdf}
\caption{The residuals, i.e., the difference between
Figures~\ref{fig:demo_logZ_H} and~\ref{fig:demo_truth}.
\label{fig:demo_residuals}}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{figures/demo_N_eff.pdf}
\caption{The error in $\ln(Z)$, expressed in terms of an
`effective number of particles' in a standard NS run that would lead to
the same error at 1 sigma. No values are below $N_{\rm eff} = 1$.
\label{fig:demo_N_eff}}
\end{figure}
